Untitled

### 2014-12-03 GEMDataSource.Rmd
Completed data merge in R

# Library required packages repmis, ridy, reshape2, and plyr packages
library(plyr)
library(repmis)
library(tidyr)
library(reshape2)
library(foreign)

@@

############# Import Annual GEM Country Level Data (means) #############

# Import GEM 2009 supportive teaching data
setwd('~/Assign2Education/GEMData')

GEM2001 <- read.spss('2001GEMNES.sav', to.data.frame = TRUE)
GEM2002 <- read.spss('2002GEMNES.sav', to.data.frame = TRUE)
GEM2003 <- read.spss('2003GEMNES.sav', to.data.frame = TRUE)
GEM2004 <- read.spss('2004GEMNES.sav', to.data.frame = TRUE)
GEM2005 <- read.spss('2005GEMNES.sav', to.data.frame = TRUE)
GEM2006 <- read.spss('2006GEMNES.sav', to.data.frame = TRUE)
GEM2007 <- read.spss('2007GEMNES.sav', to.data.frame = TRUE)
GEM2008 <- read.spss('2008GEMNES.sav', to.data.frame = TRUE)
GEM2009 <- read.spss('2009GEMNESMDS.sav', to.data.frame = TRUE)
GEM2010 <- read.spss('2010GEMNES.sav', to.data.frame = TRUE)

@@

########## Clean Annual GEM NES Datasets ##########

@@

remove(GEM2001, GEM2002, GEM2003, GEM2004, GEM2005, GEM2006, GEM2007, GEM2008, GEM2009, GEM2010)

@@

#### Merge Annual GEM data

####### Import tempfix for GEM data (created this by copying data frame (extra code for generating data frame is in misc/TrialFile.Rmd), editing outide R, and saving .csv in repository)

GEMAnnualData <- repmis::source_data("https://github.com/SamDund/Assign2Education/raw/master/GEMData/Gemyears.csv", header = TRUE, cache = FALSE)

##### Clean and merge tempfix GEM Data ####

# Change column names
names(GEMAnnualData) <- gsub("Year01", "2001", names(GEMAnnualData))
names(GEMAnnualData) <- gsub("Year02", "2002", names(GEMAnnualData))
names(GEMAnnualData) <- gsub("Year03", "2003", names(GEMAnnualData))
names(GEMAnnualData) <- gsub("Year04", "2004", names(GEMAnnualData))
names(GEMAnnualData) <- gsub("Year05", "2005", names(GEMAnnualData))
names(GEMAnnualData) <- gsub("Year06", "2006", names(GEMAnnualData))
names(GEMAnnualData) <- gsub("Year07", "2007", names(GEMAnnualData))
names(GEMAnnualData) <- gsub("Year08", "2008", names(GEMAnnualData))
names(GEMAnnualData) <- gsub("Year09", "2009", names(GEMAnnualData))
names(GEMAnnualData) <- gsub("Year10", "2010", names(GEMAnnualData))

# Change years from columns to rows and create CleanGEM
CleanGEM <- melt(data = GEMAnnualData,
                 id.vars = c("Country"),
                 measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010"))

# Rename columns
CleanGEM <- plyr::rename(x = CleanGEM,
                         replace = c("variable" = "Year",
                                     "value" = "WayofTeach"))

# Merge Clean CleanGEM with FinalGEM 
CompleteData <- merge(CleanGEM, FinalGEM,
                   union("Country", "Year"),
                   all = TRUE)

>>>>

# Library required packages repmis, ridy, reshape2, and plyr packages
library(plyr)
library(repmis)
library(tidyr)
library(reshape2)
library(foreign)
library(countrycode)

@@

@@

##################### Merge GEM Survey Data  ###################

### Insert iso2c country code for easier merging

## Add country codes and place new column at beginning of the data frame

# Create a vector of country codes
F1 <- countrycode(FinalGEM$Country, "country.name", "iso2c")

# Create a new column and insert the country code vector
FinalGEM$new.col <- F1

# Change the order of columns so country code is first
FinalGEM <- FinalGEM[,c(9,1:8)]

# Change the name of new.col
names(FinalGEM) <- gsub("new.col", "iso2c", names(FinalGEM))

##################### Import GEM NES National Survey Data  ###################

# Set working directory
setwd('~/Assign2Education/GEMData')

# Import GEM NES 2001-2010 Data
GEM2001 <- read.spss('2001GEMNES.sav', to.data.frame = TRUE)
GEM2002 <- read.spss('2002GEMNES.sav', to.data.frame = TRUE)
GEM2003 <- read.spss('2003GEMNES.sav', to.data.frame = TRUE)
GEM2004 <- read.spss('2004GEMNES.sav', to.data.frame = TRUE)
GEM2005 <- read.spss('2005GEMNES.sav', to.data.frame = TRUE)
GEM2006 <- read.spss('2006GEMNES.sav', to.data.frame = TRUE)
GEM2007 <- read.spss('2007GEMNES.sav', to.data.frame = TRUE)
GEM2008 <- read.spss('2008GEMNES.sav', to.data.frame = TRUE)
GEM2009 <- read.spss('2009GEMNESMDS.sav', to.data.frame = TRUE)
GEM2010 <- read.spss('2010GEMNES.sav', to.data.frame = TRUE)

##################### Clean GEM NES National Survey Data  ###################

@@

# Remove unnecessary dataframes from environment
remove(GEM2001, GEM2002, GEM2003, GEM2004, GEM2005, GEM2006, GEM2007, GEM2008, GEM2009, GEM2010)

@@

# Clean and cbind ataframes
dfs <- ls()[1:max(grep(pattern = 'Clean[0-1]*', x = ls()))]

for (i in dfs){
  message(i)
  temp <- get(i)
  names_temp <- names(temp)
  temp[, 'year'] <- names_temp[2]
  names(temp) <- c('Country', 'WayofTeaching', 'year')

    if (i == 'Clean01') {
      cleaned <- temp
  } else if (i != 'Clean01'){
      cleaned <- rbind(cleaned, temp)
  }
}

## Add country codes and place new column at beginning of the data frame

# Create a vector of country codes
W1 <- countrycode(cleaned$Country, "country.name", "iso2c")

# Create a new column and insert the country code vector
cleaned$new.col <- W1

# Change the order of columns so country code is first
W2 <- cleaned[,c(4,1:3)]

# Change the name of new.col
names(W2) <- gsub("new.col", "iso2c", names(W2))

# Capitalize 'year' 
names(W2) <- gsub("year", "Year", names(W2))

## Subset W2 to OECD countries

# Create matrix of OECD countries by iso2c code
myvars <- c('MX','CA','US','FR','AU','AT','BE','CL','CZ','DK','EE','FI','DE','HU', 'IS','IE','IL',
            'IT','JP','KR','LU', 'NL','NZ','NO','PL','PT','SK','SI', 'ES','SE','CH','TR','GB','US','GR')

# Subset W2 with myvars
subW2 <- subset(W2, iso2c %in% myvars)

# Delete unnecessary column
subW2$row.names <- NULL

##################### Merge two GEM Datasets  ###################

# Merge subW2 and FinalGem
CompleteData <- merge(subW2, FinalGEM,
                   union("iso2c", "Year"),
                   all = TRUE)

# Delete conflicting country names
CompleteData$Country.x <- NULL
CompleteData$Country.y <- NULL

## Add a column with country names

# Create a vector of names
C1 <- countrycode(CompleteData$iso2c, "iso2c", "country.name")

# Insert new row with C1
CompleteData$new.col <- C1

# Reorganize columns to make Country second
CompleteData <- CompleteData[,c(1,10,2:9)]

# Rename Country column
names(CompleteData) <- gsub("new.col", "Country", names(CompleteData))

### 2014-12-03 Presentation/EdEntrePres.Rmd
Attempted chart...
Completed data merge in R

@@

# Create descriptive statistics table
T1 <- stargazer(D5, type = 'html', column.sep.width = "20pt", digits = 2)
```
## Slide with Plot

>>>>

#### Wrong Datasest

@@

# Create descriptive statistics table
T1 <- stargazer(D5, type = 'html', column.sep.width = "20pt", digits = 2)
```

## WayofTeaching
```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
# Import GEM data frame
WayofTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv", header = TRUE, cache = FALSE, na.strings = "-")

## Add country codes and place new column at beginning of the data frame
# Create a vector of country codes
W1 <- countrycode(WayofTeaching$Country, "country.name", "iso2c")

# Create a new column and insert the country code vector
WayofTeaching$new.col <- W1

# Drop unnecessary column 1
WayofTeaching$X <- NULL

# Reorder columns so country code is first
W2 <- WayofTeaching[,c(10,1:9)]

# Rename first column
W3 <- plyr::rename(x = W2, 
                   replace = c("new.col" = "iso2c"))

## Slide with Plot

### 2014-12-03 Presentation/PresMisc/MiscPresStuff.Rmd
Completed data merge in R

```{r, echo=FALSE}
plot(cars)
```

>>>>

```{r, echo=FALSE}
# sankeyNetwork
library(RCurl)
library(devtools)
install_github(c('rstudio/htmltools',
            'ramnathv/htmlwidgets',
            'christophergandrud/networkD3'))
library(htmltools)
library(htmlwidgets)
library(networkD3)

URL <- "https://raw.githubusercontent.com/christophergandrud/d3Network/sankey/JSONdata/energy.json"
Energy <- getURL(URL, ssl.verifypeer = FALSE)

# Convert to data frame
EngLinks <- JSONtoDF(jsonStr = Energy, array = "links")
EngNodes <- JSONtoDF(jsonStr = Energy, array = "nodes")
